`flippant` --- An `R` package for the automated analysis of fluorescence--based

### 2017-02-03 inst/manuscript/manuscript.rmd
Remove deep referencing of Ploier et al 2016 in the main text, as requested by editorial staff;

`flippant`'s capabilities are demonstrated here by reanalyzing a subset of the
data underlying Figure 4C--F in @ploier_dimerization_2016. The first step is to
extract the data files, stored in a ZIP archive within the package.

@@

Figure \@ref(fig:figure2-creation)A emphasizes reproducibility between
independent experiments ("Experiment 1" and "Experiment 2") on the four probed
rhodopsins. Forgoing reproducibility analysis in favor of a potentially more
reliable result and following more closely the analysis in Figure 4C--F by
@ploier_dimerization_2016, a single fit may be performed for the combined data
from all experiments as follows, resulting in 
Figure \@ref(fig:figure2-creation)B:

@@

The resulting values for the fit constant correspond with
`r ppr_results_alpha_print` for `r ppr_results_names`, respectively, well to the
prior manual analysis by @ploier_dimerization_2016 (Table S2 therein), where
$\alpha \times 10^4 \approx 16$ was reported for mutant and 
$\alpha \times 10^4 \approx 7$ for wild type rhodopsin. Based on the manual
analysis of the data we conclude in @ploier_dimerization_2016 that the mutant
rhodopsins investigated are reconstituted into proteoliposomes in monomeric
form, contrary to the wild type, which is reconstituting as a homodimer. 
`flippant` analysis of the data shows identical trends and close matches of the
results, supporting identical conclusions.

>>>>

`flippant`'s capabilities are demonstrated here by reanalyzing a subset of the
data in @ploier_dimerization_2016. The first step is to extract the data files,
stored in a ZIP archive within the package.

@@

Figure \@ref(fig:figure2-creation)A emphasizes reproducibility between
independent experiments ("Experiment 1" and "Experiment 2") on the four probed
rhodopsins. Forgoing reproducibility analysis in favor of a potentially more
reliable result and following more closely the analysis by
@ploier_dimerization_2016, a single fit may be performed for the combined data
from all experiments as follows, resulting in 
Figure \@ref(fig:figure2-creation)B:

@@

The resulting values for the fit constant correspond with
`r ppr_results_alpha_print` for `r ppr_results_names`, respectively, well to the
prior manual analysis by @ploier_dimerization_2016, where
$\alpha \times 10^4 \approx 16$ was reported for mutant and 
$\alpha \times 10^4 \approx 7$ for wild type rhodopsin. Based on the manual
analysis of the data we conclude in @ploier_dimerization_2016 that the mutant
rhodopsins investigated are reconstituted into proteoliposomes in monomeric
form, contrary to the wild type, which is reconstituting as a homodimer. 
`flippant` analysis of the data shows identical trends and close matches of the
results, supporting identical conclusions.
